County Results

### 2023-06-24 reports/county_correlations.Rmd
update county results

>>>>

w_data %>%
  filter(version=="v1") %>%
  ggplot(aes(x=infections_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  theme_c() +
  labs(x = "Covidestim Estimates\n(Standardized)",
       y = "Wastewater Concentrations\n(Standardized)",
       title = "Correlations Between Wastewater Concentrations\nand Covidestim Estimates")
